### 2019-08-10 thesis.tex
included figures
* thesis.tex: Summary: saving this version for any reason

As described above, particles ejected by the Sun determine the overall
dynamics of the interplanetary space until the termination shock boundary.
Beyond this limit, the solar wind still has a significant influence on
the nature of the local interstellar space for a long distance up to the
heliopause. As a well established scientific discipline, solar and space
physics work towards developing a better understanding of this vast and
complex dynamic system called heliosphere; where, within, very close to
its most influential object, lies our home planet - Earth.

\subsection{Main topics of solar and space physics research}
\label{topics}

>>>>

As described above, particles ejected by the Sun determine the overall
dynamics of the interplanetary space until the termination shock boundary.
Beyond this limit, the solar wind still has a significant influence on
the nature of the local interstellar space for a long distance up to the
heliopause. As a well established scientific discipline, solar and space
physics work towards developing a better understanding of the Sun and
the solar processes molding this vast and complex dynamic system called
heliosphere; where, within, very close to its most influential object,
lies our home planet - Earth.

\subsection{Solar and space physics research}
\label{topics}

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{ESA_s_fleet_of_Solar_System_explorers_2019.jpg}
    \caption{ESA's past, present, and future science missions for studying the solar system.}
      {\footnotesize Credit:}
      \href{https://www.esa.int/spaceinimages/Images/2019/02/ESA_s_fleet_of_Solar_System_explorers}
      {\footnotesize ESA}{\footnotesize , accessed at 10/08/2019.}
    \label{figD1}
  \end{center}
\end{figure}

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{hso_fleet_chart_april_2019.pdf}
    \caption{NASA's present and future heliophysics system observatory. The number
      between parenthesis under the probe's name is the total number of spacecrafts
      that compose the mission.}
      {\footnotesize Credit:}
      \href{https://science.nasa.gov/heliophysics}
      {\footnotesize NASA}{\footnotesize , accessed at 10/08/2019.}
    \label{figD1}
  \end{center}
\end{figure}
